---
title: "Vignette Title"
author: "Kate McGeath"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package is an accumulation of 4 different functions that I have utilized throughout the semester.

First, the Poisson function displays different graphs of the distribution dependent on the parameters.

```{r}
output <- package::mycltp(34, 1000)
output
getwd()
```


Next, the my read function reads in data and displays it in a table.

```{r}
output2 <- package::myread(dird = "/Users/katemcgeath/Desktop/MATH4753/", "DDT.csv")
output2
```


Next, the bootstrap function creates a confidence interval for the parameters.

```{r}
ddt <- read.csv(file.choose())
output3 <- package::myboot2(x = ddt$DDT)
output3
```


Next, mymlbeta function creates maximum likelihood estimates for the parameters.

```{r}
sam = rbeta(30,shape1=3,shape2=4)
sam = sample(sam,30,replace=TRUE)
output4 <- package::mymlbeta(x = sam, alpha = seq(1, 4, length = 100), beta = seq(2, 8, length = 100), lwd = 2, labcex = 1)
output4
```

